`r glue::glue('Compare aggregated and non-aggregated reference: {params$library_id}')`

### 2025-07-08 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/reference-aggregation.Rmd

# Recode some existing colors we don't need
palette_df <- palette_df |>
  dplyr::mutate(
    label_recoded = dplyr::case_when(
      validation_group_annotation == "hematopoietic precursor cell" ~ "Neuroendocrine",
      validation_group_annotation == "muscle cell" ~ "RBCs",
      validation_group_annotation == "adipocyte" ~ "Schwann",
      validation_group_annotation == "pericyte" ~ "pDC",
      validation_group_annotation == "innate lymphoid cell" ~ "Stromal other",
      .default = validation_group_annotation
    )
  ) |>
  dplyr::filter(label_recoded %in% unique(celltype_recoded_df$label_recoded))

# Define palette
pal <- palette_df$color
names(pal) <- palette_df$label_recoded
```

>>>>

# For a set of consensus cell types that don't appear in samples this notebook explores
#  we'll grab their colors to use as NBAtlas labels.
# We'll do this by recoding cell consensus types associated with a set of colors to use, and
#  finally discard cell type labels which won't appear in the plot.
palette_df <- palette_df |>
  dplyr::mutate(
    # colors associated with these original validation groups will be now used to
    # color the given the NBAtlas cell types
    label_recoded = dplyr::case_when(
      validation_group_annotation == "hematopoietic precursor cell" ~ "Neuroendocrine",
      validation_group_annotation == "muscle cell" ~ "RBCs",
      validation_group_annotation == "adipocyte" ~ "Schwann",
      validation_group_annotation == "pericyte" ~ "pDC",
      validation_group_annotation == "innate lymphoid cell" ~ "Stromal other",
      .default = validation_group_annotation
    )
  ) |>
  # get rid of any cell types that won't appear in the plot so palette_df just contains
  # colors & cell types of interest
  dplyr::filter(label_recoded %in% unique(celltype_recoded_df$label_recoded))

# Define palette as a vector from all remaining colors/labels
pal <- palette_df$color
names(pal) <- palette_df$label_recoded
```
